---
title: "data_analysis"
author: "Chenyu Li"
format: html
editor: source
editor_options: 
  chunk_output_type: console
---

# 1 Initial setting

## 1.1 clear workspacce and set default color

```{r reset, include=FALSE}
graphics.off()
rm(list=ls(all.names=TRUE))
options(digits = 3)

options(ggplot2.discrete.colour= c("#2F7FC1", "#ff7700"))
options(ggplot2.discrete.fill= c("#2F7FC1", "#ff7700"))
```

## 1.2 Packages, theme setting and path

```{r primary setting, include=FALSE}

# package list
packages = c("tidyverse", "brms","ggpubr", "smartr","bmm","tidybayes","emmeans","bayestestR")
# get the package names that are not installed
missing_packages <- setdiff(packages, rownames(installed.packages()))
# install the missing packages
if (length(missing_packages) > 0) install.packages(missing_packages)
# library package
suppressMessages(sapply(packages, library, character.only = TRUE))


# import private functions (do not print the output)
nothing <- sapply(list.files("./functions", pattern = "*.R", full.names = TRUE), source)

# theme
theme_set(theme_bw())
dodge1 = position_dodge(.1)
dodge2 = position_dodge(.2)
dodge3 = position_dodge(.3)
dodge4 = position_dodge(.4)

theme_train <- theme(
  legend.position = "inside",
  legend.justification = c(1,0),
  legend.position.inside = c(0.98,0.02),
  strip.text = element_text(size = 11, face = "bold"),
  strip.background = element_rect(fill = "#bababa"),
  axis.text = element_text(size = 10.5),
)

theme_test <- theme(
  axis.text.y = element_blank(),
  axis.ticks.y = element_blank(),
  axis.title.y = element_blank(),
  strip.text = element_text(size = 11, face = "bold"),
  strip.background = element_rect(fill = "#bababa"),
  axis.text = element_text(size = 10.5),
)

# task name
task <- "Exp3"
model_path <- str_glue("./models/Model-{task}/Models/")
sample_path <- str_glue("./models/Model-{task}/Sample/")
figure_path <- str_glue("./figures/figures-{task}/")
log_path <- "./models/"
bf_path = "./models/BayesFactor/"

# check whether the folders are existent or not. If not, create a new one
dir.create(file.path(model_path), showWarnings = FALSE)
dir.create(file.path(sample_path), showWarnings = FALSE)
dir.create(file.path(figure_path), showWarnings = FALSE)

```


# 2 Data processing

## 2.1 Import data

```{r}

# Import Response data
Raw_Res <- read_csv("./data/Data_Exp3_Res.csv")

# Category and count response
Data_Res <- Raw_Res %>% 
  filter(screenID == "retrieval") %>% 
  mutate(
    participant = factor(participant),
    npl_trained = substring(npl_items,1, 5),
    npl_untrained = substring(npl_items,7, 11)) %>% 
  select(-npl_items) %>%
  classifyRes2(
    npl_trained = npl_trained,
    npl_untrained = npl_untrained,
    groupLevel = c("participant", "block", "trial"))

# Import Survey data
Data_Survey <- read_csv("./data/Data_Exp3_Survey.csv")

```

## 2.2 Data cleaning

```{r}

excluding_list = Data_Survey %>% 
  filter(!(str_detect(attention,"Yes") | str_detect(korean_question,"Never"))) %>% 
  pull(participant)

Data_Res <- Data_Res %>% 
  filter(
    !participant %in% excluding_list
    )

str_glue("{length(excluding_list)} participants are excluded from the analysis.") %>% message()

Data_Train <- Data_Res %>% 
  filter(expPart == "training")

Data_Test <- Data_Res %>%
  filter(expPart == "testing")

```

## 2.3 Create a table for the number of options

```{r}

# Create a table for the number of options
Table_nOptions <- data.frame(
  updPos = c("yes","no")) %>% 
  mutate(nCorrect = 1,
         nTransOld = ifelse(updPos=="yes" , 3, 2),
         nTransNew = ifelse( updPos=="yes",2,3),
         nOutSame = ifelse(updPos=="yes", 1, 1e-4),
         nOutOther = ifelse(updPos=="yes", 2, 3),
         nNPLtrained = 3,
         nNPLuntrained = 3)

# Re-frame the table
Columns_nOptions <- Table_nOptions %>% 
  pivot_longer(cols = starts_with("n"), names_to ="response", values_to = "nOpt") %>% 
  mutate(response = substring(response, 2))

# Save it for drawing the figure
write_csv(Columns_nOptions, str_glue("./figures/figures-Data/Data_{task}_nOptions.csv"))
```

# 3 Data visualization

## 3.1.1 Data and data transform

```{r}

Table_Train <- Data_Train %>% 
  select(
    participant, block, ends_with("New"), 
    ends_with("Old"), starts_with("Out"), starts_with("NPL",ignore.case=FALSE), NoRes) %>% 
  pivot_longer(
    cols = c(ends_with("New"), ends_with("Old"), starts_with("Out"), starts_with("NPL"), NoRes), 
    names_to = "response", values_to = "value") %>% 
  summarySE(DV = value, within = c("block"), between = c("response"), group = "participant") %>% 
  mutate( 
    # correct error bar
    upper = ifelse(abs(mean) < 1e-5, 0, mean + ci),
    lower = ifelse(abs(mean) < 1e-5, 0, mean - ci)) %>% 
  select(!c(ci,se,n)) %>% 
  mutate(title = "Training phase")


Table_Test_NPL <- Data_Test %>% 
  mutate(
    testItem = case_when(
      condition == "A" & updPos == "yes" ~ "Untrained",
      condition == "A" & updPos == "no" ~ "Trained",
      condition == "B" & updPos == "yes" ~ "Trained",
      condition == "B" & updPos == "no" ~ "Untrained"
    )
  ) %>% 
  select(
    participant, testItem, starts_with("NPL",ignore.case=FALSE)) %>%
  pivot_longer(
    cols = starts_with("NPL"), 
    names_to = "response", 
    values_to = "value"
    ) %>%
  summarySE(DV = value, between = c("response","testItem"), group = c("participant")) %>% 
  mutate( 
    # correct error bar
    upper = ifelse(abs(mean) < 1e-5, 0, mean + ci),
    lower = ifelse(abs(mean) < 1e-5, 0, mean - ci)) %>% 
  select(!c(ci,se,n)) %>% 
  mutate(title = "Testing phase")


Table_Test <- Data_Test %>% 
  select(
    participant, condition, updPos, ends_with("New"), ends_with("Old"), starts_with("Out")) %>% 
  pivot_longer(
    cols = c(ends_with("New"), ends_with("Old"), starts_with("Out")), 
    names_to = "response", values_to = "value") %>% 
  mutate(
    char = case_when(
      condition == "A" & response == "CorrectOld" ~ "trained",
      condition == "A" & response == "TransOld" ~ "trained",
      condition == "B" & response == "CorrectNew" ~ "trained",
      condition == "B" & response == "TransNew" ~ "trained",
      condition == "A" & str_detect(response, "Out") ~ "trained",
      
      condition == "B" & response == "CorrectOld" ~ "untrained",
      condition == "B" & response == "TransOld" ~ "untrained",
      condition == "A" & response == "CorrectNew" ~ "untrained",
      condition == "A" & response == "TransNew" ~ "untrained",
      condition == "B" & str_detect(response, "Out") ~ "untrained"),
    char = factor(
      char, 
      levels = c("trained","untrained"),
      labels = c("Familiar (Trained)","Unfamiliar (Untrained)"))
  ) %>% 
  summarySE(DV = value, within = c("char"), between = c("response","updPos"), group = "participant") %>% 
  mutate( 
    # correct error bar
    upper = ifelse(abs(mean) < 1e-5, 0, mean + ci),
    lower = ifelse(abs(mean) < 1e-5, 0, mean - ci)) %>% 
  select(!c(ci,se,n)) %>% 
  mutate(title = "Testing phase")



```

## 3.2 Correct

### 3.2.1 Training phase
```{r}
(
  Plot_Train_Correct <- Table_Train %>% 
    filter(str_detect(response,"Correct")) %>%
    mutate(
      response = factor(
        response, 
        levels = c("CorrectOld","CorrectNew"), 
        labels = c("Original items","New items"))
    ) %>% 
    ggplot(aes(x = factor(block), y = mean, group=response))+
    geom_line(
      color="#555555",
      linewidth = 0.8,
      position = dodge2)+
    geom_errorbar(
      aes(ymax = upper, ymin = lower,color=block),
      position = dodge2, 
      linewidth = 0.8,
      width = 0.2,
      show.legend = FALSE)+
    geom_point(
      aes(shape = response, fill=block),
      size = 3,
      color = "black",
      position = dodge2)+
    facet_wrap(~title, scales = "free")+
    scale_shape_manual(values = c(21,23))+
    scale_colour_gradient(low = "#ff7700",high ="#2F7FC1")+
    scale_fill_gradient(low = "#ff7700",high ="#2F7FC1")+
    scale_linetype_manual(values = c("solid","dashed"))+
    # guides(fill="none", color="none")+
    ylim(0,0.75)+
    labs(
      x = "Block", 
      y = "Proportion of correct",
      shape = "Item")+
    theme_train+
    theme(
      legend.position = "none"
    )
)


```

### 3.2.2 Testing phase

```{r}

(
  Plot_Test_Correct <- Table_Test %>% 
    filter(str_detect(response,"Correct")) %>%
    mutate(
      response = factor(
        response, 
        levels = c("CorrectOld","CorrectNew"), 
        labels = c("Original items","New items"))
    ) %>% 
    ggplot(aes(x = response, y = mean, color = char, fill=char))+
    geom_errorbar(
      aes(ymax = upper, ymin = lower),
      position = dodge2, 
      linewidth = 0.8,
      width = 0.1)+
    geom_point(
      aes(shape = response),
      size = 3,
      color = "black",
      position = dodge2)+
    facet_wrap(~title, scales = "free")+
    ylim(0,0.75)+
    scale_shape_manual(values = c(21,23))+
    scale_color_manual(values = c("#2F7FC1","#ff7700"))+
    scale_fill_manual(values = c("#2F7FC1","#ff7700"))+
    guides(fill="none")+
    labs(
      x = "Item", color = "Condition", shape = "Item")+
    theme_test
)



```


### 3.2.3 Combine

```{r}

Plot_Correct <- ggarrange(
  Plot_Train_Correct,
  Plot_Test_Correct,
  ncol = 2,
  nrow = 1,
  common.legend = FALSE
)


ggsave(
  plot = Plot_Correct,
  path = figure_path,
  filename = "Plot_Res_Correct.pdf",
  width = 9, height = 5
)

```


## 3.3 Transpositions

### 3.3.1 Training phase

```{r}
(
  Plot_Train_Trans <- Table_Train %>% 
    filter(str_detect(response,"Trans")) %>%
    mutate(
      response = factor(
        response, 
        levels = c("TransOld","TransNew"), 
        labels = c("Original items","New items"))
    ) %>% 
    ggplot(aes(x = factor(block), y = mean, group=response))+
    geom_line(
      color="#555555",
      linewidth = 0.8,
      position = dodge2)+
    geom_errorbar(
      aes(ymax = upper, ymin = lower,color=block),
      position = dodge2, 
      linewidth = 0.8,
      width = 0.2,
      show.legend = FALSE)+
    geom_point(
      aes(shape = response, fill=block),
      size = 3,
      color = "black",
      position = dodge2)+
    facet_wrap(~title, scales = "free")+
    scale_shape_manual(values = c(21,23))+
    scale_colour_gradient(low = "#ff7700",high ="#2F7FC1")+
    scale_fill_gradient(low = "#ff7700",high ="#2F7FC1")+
    scale_linetype_manual(values = c("solid","dashed"))+
    guides(fill="none", color="none")+
    ylim(0,0.25)+
    labs(
      x = "Block", 
      y = "Proportion of response",
      linetype = "Item")+
    theme_train+
    theme(
      legend.position = "none")
)

```

### 3.3.2 Testing phase

```{r}

(
  Plot_Test_Trans <- Table_Test %>% 
    filter(str_detect(response,"Trans")) %>%
    mutate(
      response = factor(
        response, 
        levels = c("TransOld","TransNew"), 
        labels = c("Original items","New items"))
    ) %>% 
    ggplot(aes(x = response, y = mean, color = char, fill=char))+
    geom_errorbar(
      aes(ymax = upper, ymin = lower),
      position = dodge2, 
      linewidth = 0.8,
      width = 0.1)+
    geom_point(
      aes(shape = response),
      size = 3,
      color = "black",
      position = dodge2)+
    facet_wrap(~title, scales = "free")+
    ylim(0,0.25)+
    scale_shape_manual(values = c(21,23))+
    guides(fill="none")+
    labs(
      x = "Item",
      shape = "Item",
      color = "Condition")+
    theme_test
)

```


### 3.3.3 Combine

```{r}

Plot_Trans <- ggarrange(
  Plot_Train_Trans,
  Plot_Test_Trans,
  ncol = 2,
  nrow = 1,
  common.legend = FALSE
)


ggsave(
  plot = Plot_Trans,
  path = figure_path,
  filename = "Plot_Res_Trans.pdf",
  width = 9, height = 5
)

```


## 3.4 Outdated items

### 3.4.1 Training phase
```{r}
(
  Plot_Res_Out <- Table_Train %>% 
    filter(str_detect(response,"Out")) %>%
    mutate(
      response = factor(
        response, 
        levels = c("OutSame","OutOther"), 
        labels = c("Original position","Other positions"))
    ) %>% 
    ggplot(aes(x = factor(block), y = mean, group = response))+
    geom_line(
      color="#555555",
      linewidth = 0.8,
      position = dodge2)+
    geom_errorbar(
      aes(ymax = upper, ymin = lower,color=block),
      position = dodge2, 
      linewidth = 0.8,
      width = 0.2,
      show.legend = FALSE)+
    geom_point(
      aes(shape = response, fill=block),
      size = 3,
      color = "black",
      position = dodge2)+
    facet_wrap(~title, scales = "free")+
    scale_shape_manual(values = c(21,23))+
    scale_colour_gradient(low = "#ff7700",high ="#2F7FC1")+
    scale_fill_gradient(low = "#ff7700",high ="#2F7FC1")+
    scale_linetype_manual(values = c("solid","dashed"))+
    ylim(0,0.2)+
    labs(
      x = "Block", 
      y = "Proportion of response",
      linetype = "Position")+
    theme_train+
    theme(
      legend.position = "none")
)

```


### 3.4.2 Testing phase

```{r}

(
  Plot_Test_Out <- Table_Test %>% 
    filter(str_detect(response,"Out")) %>%
    mutate(
      response = factor(
        response, 
        levels = c("OutSame","OutOther"), 
        labels = c("Original position","Other positions"))
    ) %>% 
    ggplot(aes(x = response, y = mean, color = char, fill=char))+
    geom_errorbar(
      aes(ymax = upper, ymin = lower),
      position = dodge2, 
      linewidth = 0.8,
      width = 0.1)+
    geom_point(
      aes(shape = response),
      size = 3,
      color = "black",
      position = dodge2)+
    facet_wrap(~title, scales = "free")+
    ylim(0,0.25)+
    scale_shape_manual(values = c(21,23))+
    scale_color_manual(values = c("#2F7FC1","#ff7700"))+
    scale_fill_manual(values = c("#2F7FC1","#ff7700"))+
    guides(fill="none")+
    labs(
      x = "Position",
      shape = "Position",
      color = "Condition")+
    theme_test
)


```

### 3.4.3 Combine

```{r}

Plot_Out <- ggarrange(
  Plot_Res_Out,
  Plot_Test_Out,
  ncol = 2,
  nrow = 1,
  common.legend = FALSE
)

ggsave(
  plot = Plot_Out,
  path = figure_path,
  filename = "Plot_Res_Out.pdf",
  width = 9, height = 5
)

```


## 3.5 NPL

### 3.5.1 Training phase

```{r}
(
  Plot_Train_NPL <- Table_Train %>% 
    filter(str_detect(response,"NPL")) %>%
    mutate(
      response = factor(
        response, 
        levels = c("NPLtrained","NPLuntrained"), 
        labels = c("NPL (Trained)","NPL (Untrained)"))
    ) %>% 
    ggplot(aes(
      x = factor(block), y = mean, 
      group=response, color = response, fill = response))+
    geom_line(
      color="#555555",
      linewidth = 0.8,
      position = dodge2)+
    geom_errorbar(
      aes(ymax = upper, ymin = lower),
      position = dodge2, 
      linewidth = 0.8,
      width = 0.2,
      show.legend = FALSE)+
    geom_point(
      aes(shape = response),
      size = 3,
      color = "black",
      position = dodge2)+
    facet_wrap(~title, scales = "free")+
    scale_shape_manual(values = c(21,23))+
    scale_linetype_manual(values = c("solid","dashed"))+
    guides(fill="none", color="none")+
    ylim(0,0.15)+
    labs(
      x = "Block", 
      y = "Proportion of response",
      linetype = "Response")+
    theme_train+
    theme(
      legend.position = "none")
)



```

### 3.5.2 Testing phase

```{r}
(
  Plot_Test_NPL <- Table_Test_NPL %>% 
    mutate(
      response = factor(
        response, 
        levels = c("NPLtrained","NPLuntrained"), 
        labels = c("NPL (Trained)","NPL (Untrained)"))
    ) %>% 
    ggplot(aes(x = testItem, y = mean, color = response, fill=response))+
    geom_errorbar(
      aes(ymax = upper, ymin = lower),
      position = dodge2, 
      linewidth = 0.8,
      width = 0.1)+
    geom_point(
      aes(shape = response),
      size = 3,
      color = "black",
      position = dodge2)+
    facet_wrap(~title, scales = "free")+
    ylim(0,0.15)+
    scale_shape_manual(values = c(21,23))+
    # guides(fill="none")+
    labs(
      x = "Tested item",
      fill = "Response category",
      shape = "Response category",
      color = "Response category")+
    theme_test
)

```

### 3.5.3 Combine

```{r}

Plot_NPL <- ggarrange(
  Plot_Train_NPL,
  Plot_Test_NPL,
  ncol = 2,
  nrow = 1,
  common.legend = FALSE
)


ggsave(
  plot = Plot_NPL,
  path = figure_path,
  filename = "Plot_Res_NPL.pdf",
  width = 9, height = 5
)

```


# 4 Model fit

## 4.1 Learning effect

### 4.1.1 Data and data transform

```{r}

# Data -------------------------------------------------------------------------

mData_Res <- Data_Res %>% 
  pivot_longer(
    cols = c(CorrectNew, CorrectOld, TransNew, TransOld, OutSame, OutOther, NPL),
    names_to = "category",
    values_to = "value"
  ) %>%
  summarize(
    Resp = sum(value, na.rm = TRUE),
    nResp = sum(!is.na(value)),
    .by = c(participant, block, category)
  ) %>% 
  mutate(
    itemType = case_when(
      str_detect(category, "Old") ~ "Original",
      str_detect(category, "New") ~ "New",
      str_detect(category, "Out") ~ "Outdated",
      TRUE ~ "NPL"),
    response = case_when(
      str_detect(category, "Correct|Same") ~ "correct",
      TRUE ~ "incorrect"),
    t = block - 1
    )

# Arguments --------------------------------------------------------------------

Args_response <- list(
  formula = Resp | trials(nResp) ~ 1 + itemType*t + (1 + itemType*t || participant),
  family = binomial(),
  prior = c(prior(normal(0,1), class = "b"), 
            prior(student_t(3, 0, 2), class = "sd", lb = 0)),
  chains = 8,
  iter = 10000,
  warmup = 2500,
  cores = 8,
  control = list(adapt_delta = 0.95, max_treedepth = 15),
  save_pars = save_pars(all = TRUE)
)

```

### 4.1.2 Correct responses

```{r}

mData_Res_Correct <- mData_Res %>% 
  filter(response == "correct",itemType %in% c("Original","New")) %>% 
  mutate(itemType = factor(itemType))

contrasts(mData_Res_Correct$itemType) = bayestestR::contr.equalprior(n = 2)

smart_runFun(
  fun = brm,
  args = Args_response %>% append(list(
      data = mData_Res_Correct,
      file = str_glue("{model_path}Model_{task}_Correct.rds"))),
  untilFinished = FALSE,
  name = "Model_Exp2_Correct",
)


Model_Correct <- readRDS(str_glue("{model_path}Model_{task}_Correct.rds"))
smart_runFun(
  fun = unupdate,
  args = list(model = Model_Correct),
  untilFinished = TRUE,
  export = "Prior_Correct"
)
bf_parameters(Model_Correct, Prior_Correct)



'
Parameter   |     BF
--------------------
(Intercept) |  0.053
itemType1   | 620.71 # main effect of the item type
t           | 115.21 # main effect of the block (leanring effect)
itemType1:t |  0.058 # interaction
'


```


## 4.2 Memory Measurement Model

### 4.2.1 Data and data transform

```{r}

mData_M3_train <- Data_Train %>% 
  tidy_M3(
    responses = c("Correct", "TransOld", "TransNew", "OutSame", "OutOther", "NPLtrained", "NPLuntrained"),
    group = c("participant", "updPos", "block"),
    DV_name = "y",
    nDV_name = "nRet",
    DV_numerical = TRUE
  ) %>% 
  left_join(Table_nOptions, by = "updPos") %>% 
  mutate(
    t = block - 1,
    iP = ifelse(updPos == "yes", 1, 0),
    condition = factor(block)
  )

mData_M3_test <- Data_Test %>% 
  tidy_M3(
    responses = c("Correct", "TransOld", "TransNew", "OutSame", "OutOther", "NPLtrained", "NPLuntrained"),
    group = c("participant", "updPos", "condition"),
    DV_name = "y",
    nDV_name = "nRet",
    DV_numerical = TRUE
  ) %>% 
  left_join(Table_nOptions, by = "updPos") %>% 
  mutate(
    condition = factor(condition),
    iP = ifelse(updPos == "yes", 1, 0),
    iM = case_when(
      condition == "A" & updPos == "no" ~ 1,
      condition == "A" & updPos == "yes" ~ 0,
      condition == "B" & updPos == "no" ~ 0,
      condition == "B" & updPos == "yes" ~ 1
    )
  )

```


### 4.2.2 Function

```{r}

genM3Form <- function(phase="train",test="linear") {
  
  if (phase=="train") {
    if (test=="linear") {
      M3_formula <- bf(
        y | trials(nRet) ~ Correct + log(nCorrect),
        nlf(mu2 ~ TransOld + log(nTransOld)),
        nlf(mu3 ~ TransNew + log(nTransNew)),
        nlf(mu4 ~ OutSame + log(nOutSame)),
        nlf(mu5 ~ OutOther + log(nOutOther)),
        nlf(mu6 ~ NPLtrained + log(nNPLtrained)),
        nlf(mu7 ~ NPLuntrained + log(nNPLuntrained)),
        nlf(Correct ~ (1-iP)*(a1 + c1) + iP*(a2 + c2) + b2),
        nlf(TransOld ~ a1 + b2),
        nlf(TransNew ~ a2 + b2),
        nlf(OutSame ~ iP*(ra*a1 + rc*c1 + b2) + (1-iP)*(-100)),
        nlf(OutOther ~ ra*a1 + b2),
        nlf(NPLtrained ~ b2),
        nlf(NPLuntrained ~ b1),
        nlf(a1 ~ ya1 + ba1*t),
        nlf(a2 ~ ya2 + ba2*t),
        nlf(c1 ~ yc1 + bc1*t),
        nlf(c2 ~ yc2 + bc2*t),
        nlf(ra ~ inv_logit(yra + bra*t)),
        nlf(rc ~ inv_logit(yrc + brc*t)),
        nlf(b2 ~ b + g*t),
        nlf(b1 ~ b),
        ya1 ~ 1 + (1 || participant),
        ba1 ~ 1 + (1 || participant),
        ya2 ~ 1 + (1 || participant),
        ba2 ~ 1 + (1 || participant),
        yc1 ~ 1 + (1 || participant),
        bc1 ~ 1 + (1 || participant),
        yc2 ~ 1 + (1 || participant),
        bc2 ~ 1 + (1 || participant),
        yra ~ 1 + (1 || participant),
        bra ~ 1 + (1 || participant),
        yrc ~ 1 + (1 || participant),
        brc ~ 1 + (1 || participant),
        g ~ 1 + (1 || participant),
        b ~ 1,
        nl = TRUE
    )
    #   M3_formula <- bf(
    #     y | trials(nRet) ~ Correct + log(nCorrect),
    #     nlf(mu2 ~ TransOld + log(nTransOld)),
    #     nlf(mu3 ~ TransNew + log(nTransNew)),
    #     nlf(mu4 ~ OutSame + log(nOutSame)),
    #     nlf(mu5 ~ OutOther + log(nOutOther)),
    #     nlf(mu6 ~ NPLtrained + log(nNPLtrained)),
    #     nlf(mu7 ~ NPLuntrained + log(nNPLuntrained)),
    #     nlf(Correct ~ (1-iP)*(a + c1) + iP*(a + c2) + b2),
    #     nlf(TransOld ~ a + b2),
    #     nlf(TransNew ~ a + b2),
    #     nlf(OutSame ~ iP*(ra*a + rc*c1 + b2) + (1-iP)*(-100)),
    #     nlf(OutOther ~ ra*a + b2),
    #     nlf(NPLtrained ~ b2),
    #     nlf(NPLuntrained ~ b1),
    #     nlf(a ~ ya + (sa - ya)*(inv_logit(exp(ba)*t)-0.5)*2),
    #     nlf(c1 ~ yc1 + (sc1 - yc1)*(inv_logit(exp(bc1)*t)-0.5)*2),
    #     nlf(c2 ~ yc2 + (sc2 - yc2)*(inv_logit(exp(bc2)*t)-0.5)*2),
    #     nlf(ra ~ inv_logit(yra + bra*t)),
    #     nlf(rc ~ inv_logit(yrc + brc*t)),
    #     nlf(b2 ~ b + g*t),
    #     nlf(b1 ~ b),
    #     ya ~ 1 + (1 || participant),
    #     sa ~ 1 + (1 || participant),
    #     ba ~ 1 + (1 || participant),
    #     yc1 ~ 1 + (1 || participant),
    #     sc1 ~ 1 + (1 || participant),
    #     bc1 ~ 1 + (1 || participant),
    #     yc2 ~ 1 + (1 || participant),
    #     sc2 ~ 1 + (1 || participant),
    #     bc2 ~ 1 + (1 || participant),
    #     yra ~ 1 + (1 || participant),
    #     bra ~ 1 + (1 || participant),
    #     yrc ~ 1 + (1 || participant),
    #     brc ~ 1 + (1 || participant),
    #     g ~ 1 + (1 || participant),
    #     b ~ 1,
    #     nl = TRUE
    # )
    } else {
      M3_formula <- bf(
        y | trials(nRet) ~ Correct + log(nCorrect),
        nlf(mu2 ~ TransOld + log(nTransOld)),
        nlf(mu3 ~ TransNew + log(nTransNew)),
        nlf(mu4 ~ OutSame + log(nOutSame)),
        nlf(mu5 ~ OutOther + log(nOutOther)),
        nlf(mu6 ~ NPLtrained + log(nNPLtrained)),
        nlf(mu7 ~ NPLuntrained + log(nNPLuntrained)),
        nlf(Correct ~ (1-iP)*(a1 + c1) + iP*(a2 + c2) + b2),
        nlf(TransOld ~ a1 + b2),
        nlf(TransNew ~ a2 + b2),
        nlf(OutSame ~ iP*(inv_logit(ra)*a1 + inv_logit(rc)*c1 + b2) + (1-iP)*(-100)),
        nlf(OutOther ~ inv_logit(ra)*a1 + b2),
        nlf(NPLtrained ~ b2),
        nlf(NPLuntrained ~ b1),
        nlf(b2 ~ b + g),
        nlf(b1 ~ b),
        a1 ~ 0 + condition + (0 + condition || participant),
        c1 ~ 0 + condition + (0 + condition || participant),
        a2 ~ 0 + condition + (0 + condition || participant),
        c2 ~ 0 + condition + (0 + condition || participant),
        ra ~ 0 + condition + (0 + condition || participant),
        rc ~ 0 + condition + (0 + condition || participant),
        g ~ 0 + condition + (0 + condition || participant),
        b ~ 1,
        nl = TRUE
      )
    }
    
  } else {
    # M3_formula <- bf(
    #     y | trials(nRet) ~ Correct + log(nCorrect),
    #     nlf(mu2 ~ TransOld + log(nTransOld)),
    #     nlf(mu3 ~ TransNew + log(nTransNew)),
    #     nlf(mu4 ~ OutSame + log(nOutSame)),
    #     nlf(mu5 ~ OutOther + log(nOutOther)),
    #     nlf(mu6 ~ NPLtrained + log(nNPLtrained)),
    #     nlf(mu7 ~ NPLuntrained + log(nNPLuntrained)),
    #     nlf(Correct ~ (1-iP)*(a1 + c1) + iP*(a2 + c2) + g + iM*b2 + (1-iM)*b1),
    #     nlf(TransOld ~ a1 + (1-iP)*g + iC*b2 + (1-iC)*b1),
    #     nlf(TransNew ~ a2 + iP*g + iC*b1 + (1-iC)*b2),
    #     nlf(OutSame ~ iP*(inv_logit(ra)*a1 + inv_logit(rc)*c1 + iC*b2 + (1-iC)*b1) + (1-iP)*(-100)),
    #     nlf(OutOther ~ inv_logit(ra)*a1 + (1-iP)*g + iC*b2 + (1-iC)*b1),
    #     nlf(NPLtrained ~ b2 + iM*g),
    #     nlf(NPLuntrained ~ b1 + (1-iM)*g),
    #     # nlf(b2 ~ b + bb),
    #     nlf(b2 ~ b),
    #     nlf(b1 ~ b),
    #     a1 ~ 0 + condition + (0 + condition || participant),
    #     c1 ~ 0 + condition + (0 + condition || participant),
    #     a2 ~ 0 + condition + (0 + condition || participant),
    #     c2 ~ 0 + condition + (0 + condition || participant),
    #     ra ~ 0 + condition + (0 + condition || participant),
    #     rc ~ 0 + condition + (0 + condition || participant),
    #     g ~ 1 + (1 || participant),
    #     # bb ~ 1 + (1 || participant),
    #     b ~ 1,
    #     nl = TRUE
    #   )
    # M3_formula <- bf(
    #     y | trials(nRet) ~ Correct + log(nCorrect),
    #     nlf(mu2 ~ TransOld + log(nTransOld)),
    #     nlf(mu3 ~ TransNew + log(nTransNew)),
    #     nlf(mu4 ~ OutSame + log(nOutSame)),
    #     nlf(mu5 ~ OutOther + log(nOutOther)),
    #     nlf(mu6 ~ NPLtrained + log(nNPLtrained)),
    #     nlf(mu7 ~ NPLuntrained + log(nNPLuntrained)),
    #     nlf(Correct ~ (1-iP)*(a1 + c1) + iP*(a2 + c2) + g + b),
    #     nlf(TransOld ~ a1 + (1-iP)*g + b),
    #     nlf(TransNew ~ a2 + iP*g + b),
    #     nlf(OutSame ~ iP*(inv_logit(ra)*a1 + inv_logit(rc)*c1 + b) + (1-iP)*(-100)),
    #     nlf(OutOther ~ inv_logit(ra)*a1 + (1-iP)*g + b),
    #     nlf(NPLtrained ~ b + iM*g),
    #     nlf(NPLuntrained ~ b + (1-iM)*g),
    #     a1 ~ 0 + condition + (0 + condition || participant),
    #     c1 ~ 0 + condition + (0 + condition || participant),
    #     a2 ~ 0 + condition + (0 + condition || participant),
    #     c2 ~ 0 + condition + (0 + condition || participant),
    #     ra ~ 0 + condition + (0 + condition || participant),
    #     rc ~ 0 + condition + (0 + condition || participant),
    #     g ~ 0 + condition + (0 + condition || participant),
    #     b ~ 1,
    #     nl = TRUE
    #   )
    M3_formula <- bf(
        y | trials(nRet) ~ Correct + log(nCorrect),
        nlf(mu2 ~ TransOld + log(nTransOld)),
        nlf(mu3 ~ TransNew + log(nTransNew)),
        nlf(mu4 ~ OutSame + log(nOutSame)),
        nlf(mu5 ~ OutOther + log(nOutOther)),
        nlf(mu6 ~ NPLtrained + log(nNPLtrained)),
        nlf(mu7 ~ NPLuntrained + log(nNPLuntrained)),
        nlf(Correct ~ (1-iP)*(a1 + c1) + iP*(a2 + c2) + b),
        nlf(TransOld ~ a1 + b),
        nlf(TransNew ~ a2 + b),
        nlf(OutSame ~ iP*(inv_logit(ra)*a1 + inv_logit(rc)*c1 + b) + (1-iP)*(-100)),
        nlf(OutOther ~ inv_logit(ra)*a1 + b),
        nlf(NPLtrained ~ b),
        nlf(NPLuntrained ~ b),
        a1 ~ 0 + condition + (0 + condition || participant),
        c1 ~ 0 + condition + (0 + condition || participant),
        a2 ~ 0 + condition + (0 + condition || participant),
        c2 ~ 0 + condition + (0 + condition || participant),
        ra ~ 0 + condition + (0 + condition || participant),
        rc ~ 0 + condition + (0 + condition || participant),
        b ~ 1,
        nl = TRUE
      )
    
  }
  
  return (M3_formula)
}

genM3Prior <- function(phase="train", test="linear") {
  
    if (phase == "train" & test=="linear") {
      M3_prior <- c(
        prior(normal(3,1), class = "b", nlpar = "ya1"),
        prior(normal(0,0.5), class = "b", nlpar = "ba1"),
        prior(normal(3,1), class = "b", nlpar = "ya2"),
        prior(normal(0,0.5), class = "b", nlpar = "ba2"),
        prior(normal(3,1), class = "b", nlpar = "yc1"),
        prior(normal(0,0.5), class = "b", nlpar = "bc1"),
        prior(normal(3,1), class = "b", nlpar = "yc2"),
        prior(normal(0,0.5), class = "b", nlpar = "bc2"),
        prior(logistic(0,1), class = "b", nlpar = "yra"),
        prior(normal(0,1), class = "b", nlpar = "bra"),
        prior(logistic(0,1), class = "b", nlpar = "yrc"),
        prior(normal(0,1), class = "b", nlpar = "brc"),
        prior(normal(0, 0.5), class = "b", nlpar = "g"),
        prior(constant(0), class = "b", nlpar = "b")
      )
      # M3_prior <- c(
      #   prior(normal(3,1), class = "b", nlpar = "ya", lb = 0),
      #   prior(normal(3,1), class = "b", nlpar = "sa", lb = 0),
      #   prior(normal(0,0.5), class = "b", nlpar = "ba"),
      #   prior(normal(3,1), class = "b", nlpar = "yc1", lb = 0),
      #   prior(normal(3,1), class = "b", nlpar = "sc1", lb = 0),
      #   prior(normal(0,0.5), class = "b", nlpar = "bc1"),
      #   prior(normal(3,1), class = "b", nlpar = "yc2", lb = 0),
      #   prior(normal(3,1), class = "b", nlpar = "sc2", lb = 0),
      #   prior(normal(0,0.5), class = "b", nlpar = "bc2"),
      #   prior(logistic(0,1), class = "b", nlpar = "yra"),
      #   prior(normal(0,1), class = "b", nlpar = "bra"),
      #   prior(logistic(0,1), class = "b", nlpar = "yrc"),
      #   prior(normal(0,1), class = "b", nlpar = "brc"),
      #   prior(normal(0, 0.5), class = "b", nlpar = "g"),
      #   prior(constant(0), class = "b", nlpar = "b")
      # )
    } else if (phase == "train" & test=="condition") {
      M3_prior <- c(
        prior(normal(3,1), class = "b", nlpar = "a1", lb = 0), 
        prior(normal(3,1), class = "b", nlpar = "a2", lb = 0), 
        prior(normal(3,1), class = "b", nlpar = "c1", lb = 0),
        prior(normal(3,1), class = "b", nlpar = "c2", lb = 0),
        prior(logistic(0,1), class = "b", nlpar = "ra"),
        prior(logistic(0,1), class = "b", nlpar = "rc"),
        prior(normal(0, 1), class = "b", nlpar = "g"),
        prior(constant(0), class = "b", nlpar = "b")
        )
    } else {
      M3_prior <- c(
        prior(normal(3,1), class = "b", nlpar = "a1", lb = 0), 
        prior(normal(3,1), class = "b", nlpar = "a2", lb = 0), 
        prior(normal(3,1), class = "b", nlpar = "c1", lb = 0),
        prior(normal(3,1), class = "b", nlpar = "c2", lb = 0),
        prior(logistic(0,1), class = "b", nlpar = "ra"),
        prior(logistic(0,1), class = "b", nlpar = "rc"),
        # prior(normal(0, 0.5), class = "b", nlpar = "bb"),
        # prior(normal(0, 1), class = "b", nlpar = "g"),
        prior(constant(0), class = "b", nlpar = "b")
        )
    }
    
 
  return (M3_prior)
}

```


### 4.2.3 Model comparison

```{r}

# Training phase ---------------------------------------------------------------

smart_runFun(
  fun = brm,
  args = list(
    formula = genM3Form(phase="train"),
    data = mData_M3_train,
    family = multinomial(refcat = NA),
    prior = genM3Prior(phase = "train"),
    chains = 8,
    cores = 8,
    iter = 10000,
    warmup = 2500,
    control = list(adapt_delta = 0.98),
    save_pars = save_pars(all = TRUE),
    sample_prior = "yes",
    init = 0,
    file = paste0(model_path, "Model_Exp3_M3_Training")
    ),
  name = "Model_Exp3_M3_Training"
)

smart_runFun(
  fun = brm,
  args = list(
    formula = genM3Form(phase="train",test="condition"),
    data = mData_M3_train,
    family = multinomial(refcat = NA),
    prior = genM3Prior(phase = "train",test="condition"),
    chains = 8,
    cores = 8,
    iter = 10000,
    warmup = 2500,
    control = list(adapt_delta = 0.98),
    save_pars = save_pars(all = TRUE),
    sample_prior = "yes",
    init = 0,
    file = paste0(model_path, "Model_Exp3_M3_Training_condition")
    ),
  name = "Model_Exp3_M3_Training_condition"
)

# Testing phase ----------------------------------------------------------------
smart_runFun(
  fun = brm,
  args = list(
    formula = genM3Form(phase="test"),
    data = mData_M3_test,
    family = multinomial(refcat = NA),
    prior = genM3Prior(phase="test"),
    chains = 8,
    cores = 8,
    iter = 10000,
    warmup = 2500,
    control = list(adapt_delta = 0.98),
    save_pars = save_pars(all = TRUE),
    sample_prior = "yes",
    init = 0,
    file = paste0(model_path, "Model_Exp3_M3_Testing_nog")
    ),
  name = "Model_Exp3_M3_Testing_nog"
)


```


### 4.2.4 Bayes factor
```{r}

Model_M3 <- read_rds(str_glue("{model_path}Model_{task}_M3_Softmax_condition.rds"))

Hypothesis <- hypothesis(Model_M3, c(
  a1 = "a1_conditionfamiliar = a1_conditionunfamiliar",
  c1 = "c1_conditionfamiliar = c1_conditionunfamiliar",
  a2 = "a2_conditionfamiliar = a2_conditionunfamiliar",
  c2 = "c2_conditionfamiliar = c2_conditionunfamiliar",
  ra = "ra_conditionfamiliar = ra_conditionunfamiliar",
  rc = "rc_conditionfamiliar = rc_conditionunfamiliar"
))

Hypothesis$hypothesis %>% mutate(Evid.Ratio = 1/Evid.Ratio)

plot(Hypothesis)

'
  Hypothesis Estimate Est.Error CI.Lower CI.Upper Evid.Ratio Post.Prob Star
1         a1   -0.144     0.120   -0.368   0.0974      0.177    0.8496     
2         c1    0.512     0.320   -0.113   1.1430      0.837    0.5444     
3         a2   -0.178     0.121   -0.414   0.0622      0.245    0.8035     
4         c2    0.751     0.236    0.288   1.2169     27.889    0.0346    *
5         ra    0.650     2.206   -3.744   5.1226      0.878    0.5323     
6         rc   -0.840     0.638   -2.303   0.2470      0.683    0.5943     
'


```


### 4.2.5 Posterior

```{r}

# Training model ---------------------------------------------------------------
Model_M3 <- read_rds(str_glue("{model_path}Model_Exp3_M3_Training.rds"))

Post_M3 <- Model_M3 %>% 
  gather_draws(`b_.*`, regex = TRUE) %>% 
  separate_wider_delim(.variable, "_", names = c(NA, "par", NA), cols_remove = TRUE) %>% 
  rename(post = .value)

# Save the posterior
write_rds(Post_M3, str_glue("./figures/figures-Data/Post_{task}_M3_Training.rds"))



# Testing ----------------------------------------------------------------------

Model_M3 <- read_rds(str_glue("{model_path}Model_Exp3_M3_Testing_baseline2.rds"))

Post_M3 <- Model_M3 %>% 
  extractPost("condition", par_name = "par") %>% 
  filter(!is.na(post), condition!="Intercept") %>% 
  mutate(
    post = ifelse(str_detect(par,"r"), inv_logit_scaled(post), post),
    condition = case_when(
      condition=="A" & par %in% c("a1","c1","ra","rc") ~ "familiar",
      condition=="B" & par %in% c("a2","c2") ~ "familiar",
      TRUE ~ "unfamiliar"
    )
  )

write_rds(Post_M3, str_glue("./figures/figures-Data/Post_{task}_M3_Testing.rds"))

```






