---
title: "data_analysis"
author: "Chenyu Li"
format: html
editor: source
editor_options: 
  chunk_output_type: console
---

# 1 Initial setting

## 1.1 clear workspacce and set default color

```{r reset, include=FALSE}
graphics.off()
rm(list=ls(all.names=TRUE))
options(digits = 3)

options(ggplot2.discrete.colour= c("#615F63","#FF7F6F","#2F7FC1","#FFBE7A","#8FC0A9","#8A1C56"))
options(ggplot2.discrete.fill= c("#615F63","#FF7F6F","#2F7FC1","#FFBE7A","#8FC0A9","#8A1C56"))
```

## 1.2 Packages, theme setting and path

```{r primary setting, include=FALSE}

# package list
packages = c("tidyverse", "brms","ggpubr", "job","tidybayes","emmeans","bayestestR")
# get the package names that are not installed
missing_packages <- setdiff(packages, rownames(installed.packages()))
# install the missing packages
if (length(missing_packages) > 0) install.packages(missing_packages)
# library package
suppressMessages(sapply(packages, library, character.only = TRUE))


# import private functions (do not print the output)
nothing <- sapply(list.files("./functions", pattern = "*.R", full.names = TRUE), source)

# theme
theme_set(theme_bw())
dodge1 = position_dodge(.1)
dodge2 = position_dodge(.2)
dodge3 = position_dodge(.3)
dodge4 = position_dodge(.4)

# task name
task <- "Exp1"
model_other_path <- str_glue("./models/Model-{task}/Models_Others/")
model_path <- str_glue("./models/Model-{task}/Models/")
sample_path <- str_glue("./models/Model-{task}/Sample/")
figure_path <- str_glue("./figures/figures-{task}/")
log_path <- "./models/"
bf_path = "./models/BayesFactor/"

# check whether the folders are existent or not. If not, create a new one
dir.create(file.path(model_path), showWarnings = FALSE)
dir.create(file.path(sample_path), showWarnings = FALSE)
dir.create(file.path(figure_path), showWarnings = FALSE)

```


# 2 Data processing

## 2.1 Import data

```{r}

# Import Response data
Raw_Res <- read_csv("./data/Data_Exp1_Res.csv")

# Category and count response
Data_Res <- Raw_Res %>% 
  filter(screenID == "retrieval") %>% 
  mutate(
    participant = factor(participant)) %>% 
  classifyRes(groupLevel = c("participant", "block", "trial"))

# Import Survey data
Data_Survey <- read_csv("./data/Data_Exp1_Survey.csv")

```

## 2.2 Data cleaning

```{r}




```

## 2.3 Create a table for the number of options

```{r}

# Create a table for the number of options
Table_nOptions <- data.frame(
  updPos = c("yes","no")) %>% 
  mutate(nCorrect = 1,
         nTransOld = ifelse(updPos=="yes" , 3, 2),
         nTransNew = case_when(
           updPos=="yes" ~ 2,
           updPos=="no" ~ 3),
         nOutSame = ifelse(updPos=="yes", 1, 1e-4),
         nOutOther = case_when(
           updPos=="yes" ~ 2, 
           updPos=="no" ~ 3),
         nNPL = 6)

# Re-frame the table
Columns_nOptions <- Table_nOptions %>% 
  pivot_longer(cols = starts_with("n"), names_to ="response", values_to = "nOpt") %>% 
  mutate(response = substring(response, 2))

# Save it for drawing the figure
write_csv(Columns_nOptions, str_glue("./figures/figures-Data/Data_{task}_nOptions.csv"))
```

# 3 Ploting data

## 3.1 Data and data transform

```{r}

Table_response <- Data_Res %>% 
  select(
    participant, condition, ends_with("New"), 
    ends_with("Old"), starts_with("Out"), NPL, NoRes) %>% 
  pivot_longer(
    cols = c(ends_with("New"), ends_with("Old"), starts_with("Out"),NPL, NoRes), 
    names_to = "response", values_to = "value") %>% 
  summarySE(DV = value, within = c("condition"), between = c("response"), group = "participant") %>% 
  mutate( 
    condition = factor(
      condition, 
      levels = c("cn","kr"), 
      labels = c("Familiar (Chinese)", "Unfamiliar (Korean)")),
    # correct error bar
    upper = ifelse(abs(mean) < 1e-5, 0, mean + ci),
    lower = ifelse(abs(mean) < 1e-5, 0, mean - ci)) %>% 
  select(!c(ci,se,n))

```


## 3.2 Plot


### 3.2.1 Correct
```{r}
(
  Plot_Res_Correct <- Table_response %>% 
    filter(str_detect(response,"Correct")) %>%
    mutate(
      response = factor(
        response, 
        levels = c("CorrectOld","CorrectNew"), 
        labels = c("Origianl items","New items"))
    ) %>% 
    ggplot(aes(x = response, y = mean, color = condition))+
    geom_point(position = dodge2)+
    geom_errorbar(aes(ymax = upper, ymin = lower),position = dodge2, width = 0.1)+
    ylim(0,1)+
    labs(
      x = "Item type", y = "Proportion of correct", 
      title = "Correct",
      color = "Condition")+
    theme(
      legend.position = "None",
      title = element_text(size = 11),
      axis.text = element_text(size = 10.5))
)





```


### 3.2.2 Transpositions
```{r}
(
  Plot_Res_Trans <- Table_response %>% 
    filter(str_detect(response,"Trans")) %>%
    mutate(
      response = factor(
        response, 
        levels = c("TransOld","TransNew"), 
        labels = c("Origianl items","New items"))
    ) %>% 
    ggplot(aes(x = response, y = mean, color = condition))+
    geom_point(position = dodge2)+
    geom_errorbar(aes(ymax = upper, ymin = lower),position = dodge2, width = 0.1)+
    ylim(0,0.3)+
    labs(
      x = "Item type", y = "Proportion of response", 
      title = "Transpositions")+
    theme(
      legend.position = "None",
      title = element_text(size = 11),
      axis.text = element_text(size = 10.5))
)

```


### 3.2.3 Outdated items
```{r}
(
  Plot_Res_Outdated <- Table_response %>% 
    filter(str_detect(response,"Out")) %>%
    mutate(
      response = factor(
        response, 
        levels = c("OutSame","OutOther"), 
        labels = c("Original position","Other positions"))
    ) %>% 
    ggplot(aes(x = "Outdated items", y = mean, color = condition))+
    geom_point(position = dodge2)+
    geom_errorbar(aes(ymax = upper, ymin = lower),position = dodge2, width = 0.1)+
    facet_wrap(~response, scales = "free")+
    labs(
      x = "", y = "Proportion of response", 
      title = "Outdated items")+
    theme(
      legend.position = "None",
      axis.text.x = element_blank(),
      axis.title = element_blank(),
      axis.ticks.x = element_blank(),
      title = element_text(size = 11),
      axis.text = element_text(size = 10.5),
      strip.text = element_text(size = 10.5))
)

scale_individual_facet_y_axes(Plot_Res_Outdated, ylims = list(c(0,0.3), c(0,0.3)))

```

### 3.2.4 NPL
```{r}
(
  Plot_Res_NPL <- Table_response %>% 
    filter(str_detect(response,"NPL")) %>%
    ggplot(aes(x = response, y = mean, color = condition))+
    geom_point(position = dodge1)+
    geom_errorbar(aes(ymax = upper, ymin = lower),position = dodge1, width = 0.1)+
    ylim(0,0.3)+
    labs(
      x = "", y = "Proportion of response", 
      title = "NPL")+
    theme(
      # legend.position = "None",
      axis.text.x = element_blank(),
      axis.title.x = element_blank(),
      axis.ticks.x = element_blank(),
      title = element_text(size = 11),
      axis.text = element_text(size = 10.5))
)


```

### 3.2.5 Combined
```{r}

Plot_Res_combined <- ggpubr::ggarrange(
  Plot_Res_Correct, Plot_Res_Trans, Plot_Res_Outdated, Plot_Res_NPL,
  ncol = 2, nrow = 2, common.legend = TRUE, legend = "right")


```


# 4 Memory Measurement Model

## 4.1 Data and data transform

```{r}

mData_M3 <- Data_Res %>% 
  tidy_M3(
    responses = c("Correct", "TransOld", "TransNew", "OutSame", "OutOther", "NPL"),
    group = c("participant", "condition", "updPos"),
    DV_name = "y",
    nDV_name = "nRet",
    DV_numerical = TRUE
  ) %>% 
  left_join(Table_nOptions, by = "updPos") %>% 
  mutate(
    iP = ifelse(updPos == "yes", 1, 0)
  )

```


## 4.2 Function

```{r}

genM3Form <- function(a1 = "free", c1 = "free", a2 = "free", 
                      c2 = "free", ra = "free", rc = "free") {
  
  if (a2=="same") a1 = "fix"
  
  if (ra=="fix") {
    form_mu4 = nlf(mu4 ~ iP*(a1 + inv_logit(rc)*c1 + n) +log(nOutSame))
    form_mu5 = nlf(mu5 ~ (a1 + n) + log(nOutOther))
    form_ra = as.formula(NULL)
  } else {
    form_mu4 = nlf(mu4 ~ iP*(inv_logit(ra)*a1 + inv_logit(rc)*c1 + n) +log(nOutSame))
    form_mu5 = nlf(mu5 ~ inv_logit(ra)*a1 + n + log(nOutOther))
    form_ra = ra ~ 0 + condition + (0 + condition || participant)
  }
  
  if (a1 == "fix"){
    form_a1 = a1 ~ 1 + (1 || participant)
  } else {
    form_a1 = a1 ~ 0 + condition + (0 + condition || participant)
  }
  
  if (a2=="fix") {
    form_a2 = a2 ~ 1 + (1 || participant)
  } else if (a2=="same") {
    form_a2 = nlf(a2 ~ a1)
  } else {
    form_a2 = a2 ~ 0 + condition + (0 + condition || participant)
  }
  
  final_form <- bf(
    y | trials(nRet) ~ (1-iP)*(a1 + c1) + iP*(a2 + c2) + n + log(nCorrect),
    nlf(mu2 ~ a1 + n + log(nTransOld)),
    nlf(mu3 ~ a2 + n + log(nTransNew)),
    form_mu4,
    form_mu5,
    nlf(mu6 ~ n + log(nNPL)),
    form_a1,
    c1 ~ 0 + condition + (0 + condition || participant),
    form_a2,
    c2 ~ 0 + condition + (0 + condition || participant),
    form_ra,
    rc ~ 0 + condition + (0 + condition || participant),
    n ~ 1,
    nl = TRUE)
  
  return (final_form)
}


genM3Prior <- function(a1="free", c1="free", a2="free", c2="free", ra="free", rc="free") {
  
  if (ra=="fix") {
    prior_ra = NULL
  } else {
    prior_ra = prior(normal(0,1), class = "b", nlpar = "ra")
  }
  
  if (a2 == "same") {
    prior_a2 = NULL
  } else {
    prior_a2 = prior(normal(3,1), class = "b", nlpar = "a2", lb = 0)
  }
  
  
  final_prior <- c(
    prior(normal(3,1), class = "b", nlpar = "a1", lb = 0), 
    prior(normal(3,1), class = "b", nlpar = "c1", lb = 0),
    prior_a2, 
    prior(normal(3,1), class = "b", nlpar = "c2", lb = 0),
    prior_ra,
    prior(normal(0,1), class = "b", nlpar = "rc"),
    prior(constant(0), class = "b", nlpar = "n"))
  
  return (final_prior)
}

```


## 4.3 Model comparison

```{r}

List_MC <- list(
  ra = c("free", "fix"),
  a2 = c("free","same")
)

# Initialize job log
init_jobLog(model_path)

seq_model_comparsion(
  task = task,
  pars = List_MC,
  form_fun = genM3Form,
  prior_fun = genM3Prior,
  brmArgs = list(
    data = mData_M3,
    family = multinomial(refcat = NA),
    chains = 4,
    cores = 4,
    iter = 5000,
    warmup = 2000,
    control = list(adapt_delta = 0.95),
    save_pars = save_pars(all = TRUE),
    sample_prior = "yes",
    init = 0),
  model_path = model_path,
  sample_path = sample_path,
  bf_path = bf_path,
  maxCore = 4,
  sample_check = TRUE
)


```


## 4.4 Bayes factor
```{r}

Model_M3 <- read_rds(str_glue("{model_path}Model_Exp1_M3_rafix_a2same.rds"))

Hypothesis <- hypothesis(Model_M3_SS6, c(
  rc_RU = "rc_conditionupdating = rc_conditionremoval",
  c1_EU = "c1_conditionencoding = c1_conditionupdating",
  c1_KR = "c1_conditionkeeping = c1_conditionremoval",
  c2_EU = "c2_conditionencoding = c2_conditionupdating"
))

plot(Hypothesis)

'
Hypothesis Tests for class b:
  Hypothesis Estimate Est.Error CI.Lower CI.Upper Evid.Ratio Post.Prob Star
1      rc_RU   -0.360     0.843  -2.0002    1.338    1.47874   0.59657     
2      c1_EU    0.639     0.280   0.0923    1.194    0.36833   0.26918    *
3      c1_KR    1.311     0.384   0.5802    2.093    0.00702   0.00697    *
4      c2_EU    0.179     0.325  -0.4548    0.821    3.68727   0.78666     
'


```


### 4.4.5 Posterior

```{r}

Table_condition <- data.frame(
  condition = rep(c("cn","kr"),times = 2),
  formCond = c("cn","kr",
               "Intercept","Intercept")) %>% 
  mutate(condition = factor(condition))


# The best model
# Model_M3_SS6 <- read_rds(str_glue("{model_path}Model_Exp1_M3_rafix_a2same.rds"))

# The original model
Model_M3_SS6 <- read_rds(str_glue("{model_path}Model_Exp1_M3_rafree_a2free.rds"))

Post_M3 <- Model_M3_SS6 %>% 
  extractPost("condition", par_name = "M3_par") %>% 
  rename(formCond = condition) %>% 
  right_join(Table_condition ,relationship = "many-to-many") %>% 
  select(!formCond) %>%
  filter(!is.na(post), M3_par!="n") %>% 
  pivot_wider(names_from = M3_par, values_from = post) %>% 
  filter(!is.na(condition)) %>% 
  rowwise() %>% 
  mutate(
    a2 = ifelse("a2" %in% names(.), a2, a1),
    ra = ifelse("ra" %in% names(.), inv_logit_scaled(ra), 1),
    rc = ifelse("rc" %in% names(.), inv_logit_scaled(rc), 0)
    ) %>% 
  ungroup() %>% 
  select(.chain, .iteration, .draw, condition, a1, a2, c1, c2, ra, rc)

# Save the posterior
write_rds(Post_M3, str_glue("./figures/figures-Data/Post_{task}_M3_initial.rds"))
# write_rds(Post_M3, str_glue("./figures/figures-Data/Post_{task}_M3_final.rds"))


```






